---
title: "Proportions and R"
author: "Dr K"
date: "February 27, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(tidyverse)
```

## Understanding proportion distributions
###Identifying when the sample proportion is nearly normal
A sample proportion can be described as a sample mean. If we represent each "success" as
a 1 and each "failure" as a 0, then the sample proportion is the mean of these numerical
outcomes:
^p =
0 + 1 + 1 + . . . + 0
1042
= 0:82
The distribution of ^p is nearly normal when the distribution of 0's and 1's is not too strongly
skewed for the sample size. The most common guideline for sample size and skew when
working with proportions is to ensure that we expect to observe a minimum number of
successes (1's) and failures (0's), typically at least 10 of each. The labels success and
failure need not mean something positive or negative. These terms are just convenient
words that are frequently used when discussing proportions  

##Conditions for the sampling distribution of ^p being nearly normal
The sampling distribution for ^p, taken from a sample of size n from a population
with a true proportion p, is nearly normal when
1. the sample observations are independent and
2. we expected to see at least 10 successes and 10 failures in our sample, i.e.
np >= 10 and n(1-p)>= 10. This is called the success-failure condition.
If these conditions are met, then the sampling distribution of ^p is nearly normal
with mean p and standard error SE = sqrt(p*(1-p)/n)

##Why are we interested in proportions? Because it is natural when dealing with categorical data

```{r}
#make up universe
Win=rep("win",times=1000)
Lose=rep("oops",times=4000)
Mix=c(Win,Lose)
```

##Now grab 50 points and take a look

```{r}
out = sample(Mix,size=50)

table(out)
  
```


### we are going to pick a sample size of 50 and repeatedly draw samples and record the proportions of win  

####This time we will make our data up with numbers 1 for won 0 for oops. Explore what happens as you change the proportion of 1's and the sample size.
    
```{r}
#make up numeric universe,
Win=rep(1,times=1000)
Lose=rep(0,times=4000)
Mix=c(Win,Lose)

    
ourProp=numeric()
samsize = 50
for(i in 1:10000){
  x<-sample(Mix,size = samsize, replace = TRUE)
    ourProp[i]<-sum(x)
}
Out <- (ourProp/samsize)*100
  histogram(Out)
  plot(density(Out))
mean(Out)
sd(Out)
```
