---
title: "Chi Squared distribution and R"
author: "Dr K"
date: "February 27, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tigerstats)
require(tidyverse)
```

## Understanding Chisq distributions
As we have seen by using the normal distribution, we were able to extend its application to that of proportions, noting that for samples carrying at least 5 observations will have their proportions distributed normally.
Second Among all the distributions we see in practice, The most common dealing with categorical data is the right-tailed chisq distribution. It is really a parameter family with a single parameter called "the degrees of freedom". They are generated by taking samples from normal(0,1) distributions then summing their squared values. The degrees of freedom comes from the size of your sample.  Let's see if we can create a collection of values that would represent a large sample from a chi3 (ie 3 df chisq distribution).

```{r}
chi3=numeric()
data=rnorm(10000)
for(i in 1:10000){
  x<-sample(data,size = 3)
  xx <- x*x
  chi3[i]<-sum(xx)
}
summary(chi3)
  histogram(chi3)
  plot(density(chi3))

```

##Now just grab 10000 points from the rchisq helper function.

```{r}
chi3=rchisq(10000,df=3)

summary(chi3)
  histogram(chi3)
  plot(density(chi3))

```


### we are going to plot Chi_Squared distributions degrees of Freedom go 3,10,15,25,30,50


```{r}
base=seq(from=0,to=100,by=.02)
chi3=dchisq(base,df=3)
chi10=dchisq(base,df=10)
chi15=dchisq(base,df=15)
chi25=dchisq(base,df=25)
chi30=dchisq(base,df=30)
chi50=dchisq(base,df=50)
plot(base,chi3,type="l")
title(main="Chi_Square plots \n Deg of freedom from 3 to 50")
lines(base,chi10,type="l",col=2)
lines(base,chi15,type="l",col=3)
lines(base,chi25,type="l",col=4)
lines(base,chi30,type="l",col=5)
lines(base,chi50,type="l",col=6)

```
    
    
## chi_squared data is right tailed and the mean is close to the degrees of freedom 


##Now go to the KHAN academy and watch the first 3 videos on Chi-square.